Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex

$$
\begin{array}{ll}
N_C(z) {=} 0z^2{+}0z{+}0\\
D_C(z) {=} 0z^2{+}0z{+}0\\
\end{array}
$$

In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.026506\\
\Delta D_G(z) = 1.000610z+1.002838
\end{array}
$$

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\begin{array}{ll}
N_C(z) {=} 12.402664z^2{-}11.439667z{+}0.596756\\
D_C(z) {=} 4.003906z^2{-}0.287949z{+}0.015625\\
\end{array}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
$$
\begin{array}{ll}
\Delta N_G(z) {=} 0.026314\\
\Delta D_G(z) {=} 0.999024z{-}1.004785
\end{array}
$$
%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

$$
\begin{array}{ll}
N_C(z) {=} 11.035202z^2{+}5.846100z{+}4.901855\\
D_C(z) {=} 1.097901z^2{+}0.063110z{+}0.128357\\
\end{array}
$$

@@

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is
}

@@

\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
holds and the inductive back-end is able to find a stable solution in less than one minute}. 
This is possible if the inductive solutions need to be refined with few counterexamples 
and fixed point precision increases. However, some of our benchmarks did not meet these criteria. 
\textcolor{red}{Which cases? Can you refer to Table~\ref{tab:results} In these cases, 
the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes}.

\begin{figure}[H]
\centering
\begin{tabular}{l | r r l}
Benchmark              & Base     & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    & 46\,s   & \\
SatelliteB2            & 7\,s     & 6601\,s & \tbmark\\
SatelliteC2            & 2\,s     & 76\,s   & \tbmark\\
SpringMassDamper       & 28\,s    & \xmark  &
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, \xmark = uncontrollable}
\vspace{0.5em}

\caption{Experimental results. \label{tab:results}}
\end{figure}
%---------------------------------

\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the majority of the benchmarks \textcolor{red}{can you be more specific? which benchmarks?}, and can be
complemented using the interval arithmetic back-end, where the inductive conjectures fail
too frequently. Both back-ends enabled controller synthesis for all benchmarks within
reasonable time frames.

>>>>

%$$
%\begin{array}{ll}
%N_C(z) {=} 0z^2{+}0z{+}0\\
%D_C(z) {=} 0z^2{+}0z{+}0\\
%\end{array}
%$$
$$
\blue{
C(z)=\frac{0z^2{+}0z{+}0}{0z^2{+}0z{+}0}
}
$$

In the first {\sc verify} phase we obtain the following counterexample:

$$
\blue{
\Delta{\vec{p}} = [0.026506~ 1.000610~ 1.002838]^T
}
$$

%$$
%\begin{array}{ll}
%\Delta N_G(z) = 0.026506\\
%\Delta D_G(z) = 1.000610z+1.002838
%\end{array}
%$$

We add this counterexample to {\sc inputs} and initiate the {\sc synthesise} phase, where we get the following candidate solution: 
%\red{[ How is the order of the candidate solution chosen here?]}
$$
\blue{
C(z)=\frac{12.402664z^2{-}11.439667z{+}0.596756}{4.003906z^2{-}0.287949z{+}0.015625}
}
$$

In the second {\sc verify} phase, we check whether the current candidate
solution above is the final solution. It is not and the verifier signals
that it is due to lack of precision. We thus increase our precision to
$I_b=20,F_b=28$.
%
We stay in the {\sc verify} phase and receive a new counterexample at
higher precision:
\cdsay{Pascal, this sounds confusing. if you want to increase precision on-the-fly, i.e. 
not going back to the synthesise phase, 
then this illustration doesn't follow the general diagram in Fig.5. 
We need to decide which direction we keep.}
%
%$$
%\begin{array}{ll}
%\Delta N_G(z) {=} 0.026314\\
%\Delta D_G(z) {=} 0.999024z{-}1.004785
%\end{array}
%$$
$$
\blue{
\Delta{\vec{p}} = [0.026314~ 0.999024~ {-}1.004785]^T
}
$$

%\blue{[Nice, now I'm in the groove. Next unfolds well.] }
Since previous counterexamples were attained at lower precision, we 
remove them from the counterexample set. In the next {\sc synthesise}
phase, we get a new candidate solution that holds for the newly
inserted counterexample:

$$
\blue{
C(z)=\frac{11.035202z^2{+}5.846100z{+}4.901855}{1.097901z^2{+}0.063110z{+}0.128357}
}
$$
%
%$$
%\begin{array}{ll}
%N_C(z) {=} \\
%D_C(z) {=} \\
%\end{array}
%$$

@@

\blue{Initially, the controller denominator and numerator  ($D_{C}(z)$ and $N_{C}(z)$) are started with zero coefficients, as in previous example. Thus,  in the first {\sc verify} phase a counterexample is presented, that is added to {\sc inputs}, whis is usede in the first  {\sc synthesise} phase. The resulting controller is:
}
$$
{
\blue{
C(z)=\frac{0.77516z^2{+}-0.71497z{+}0.03729}{0.25024z^2{-}0.01799z{+}0.00097}
}}
$$

\blue{In the second {\sc verify} phase, the controller failed to stabilize the system for all the range of uncertainties, another counterexample was provided, and the following candidate controller is presented in another {\sc synthesise} phase:}
$$
{
\blue{
C(z)=\frac{0.68970z^2{+}0.36538z{+}0.30637}{0.06862z^2{+}0.00394z{+}0.00802}
}}
$$

\blue{
This candidate solution is validated as the final solution by the next 
{\sc verify} phase.
}

@@

\textcolor{red}{How did you obtain the results from Table~\ref{tab:results}? 
Can you provide the command-line? The reviewers should be able to reproduce our experiments.}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. \textcolor{red}{Which section do you refer??
For most benchmarks the conjecture explained in section~\ref{fixedpoint_verification} 
holds and the inductive back-end is able to find a stable solution in less than one minute}. 
This is possible if the inductive solutions need to be refined with few counterexamples 
and fixed point precision increases. However, two benchmarks in our set did not meet these
criteria (marked with $^*$ in Table~\ref{tab:results}). In these cases, 
the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.

\textcolor{red}{Can you relate the benchmarks in Table~\ref{tab:results} in terms of 
$C$ and $G$ as described in section~\ref{experimental-setup}. You could add an additional column to that table.}

\begin{table}[H]
\centering
\begin{tabular}{l | r l}
Benchmark                 & Base    & \\\cline{1-2}
CruiseControl02           & 17\,s   & \\
CruiseControl02$^\dagger$ & 46\,s   & \\
SatelliteB2               & 7\,s    & \\
SatelliteB2$^\dagger$     & 6601\,s & \tbmark\\
SatelliteC2               & 2\,s    & \\
SatelliteC2$^\dagger$     & 76\,s   & \tbmark\\
SpringMassDamper          & 28\,s   & \\
a\_PL1\_SCH2\_IMPL1       & 2704\,s & \\
a\_PL1\_SCH2\_IMPL2       & 538\,s  & \\
a\_PL1\_SCH2\_IMPL3       & 12\,s   & \\
a\_PL1\_SCH3\_IMPL1       & 318\,s  & \\
a\_PL1\_SCH3\_IMPL2       & 967\,s  & \\
a\_PL1\_SCH3\_IMPL3       & 9798\,s & \\
a\_PL1\_SCH4\_IMPL1       & 6304\,s & \\
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end, $\dagger$ = with uncertainty}
\vspace{0.5em}

\caption{Experimental results. \label{tab:results}}
\end{table}
%---------------------------------

\textcolor{red}{Can you provide the synthesised controllers? Iury could then check the solution using the bode diagram.}
We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the 12 out of 14 benchmarks, and can be
complemented using the interval arithmetic back-end for the remaining 2 benchmarks,
where the inductive conjectures fail too frequently. Both back-ends together enabled controller
synthesis for all benchmarks within reasonable time frames.
